Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-04 draft/accordionComplexSurfaces.tex
cleaning captions figures
Non-kissing = non-crossing (except for figures).

\begin{lemma}
\label{lem:nonKissing=nonCrossing}
Non-kissing walks = non-crossing $\dissection$-accordion curves.
\end{lemma}

\begin{theorem}
\label{thm:complexesCoincide}
\begin{itemize}
\item For any locally gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$, therefore to the accordion complex~$\AC[\dissection_{\bar Q}]$ and to the slalom complex~$\SC[{\dissection_{\bar Q}}\dual]$.
\item For any pair of dual cellular dissections~$\dissection, \dissection\dual$ of an oriented surface, the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
\end{itemize}
\end{theorem}

>>>>

\begin{lemma}
\label{lem:nonKissing=nonCrossing}
Let~$\omega_1$ and~$\omega_2$ be walks on~$\bar Q$.  Then~$\omega_1$ and~$\omega_2$ are non-kissing if and only if the~$\dissection_{\bar Q}$-accordions~$\curveof(\omega_1)$ and~$\curveof(\omega_2)$ are non-crossing on~$\surface(\bar Q)$.
\end{lemma}
\begin{proof}
 \pierreguy{Picture No.4}
\end{proof}

\begin{theorem}
\label{thm:complexesCoincide}
\begin{itemize}
\item For any locally gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$, therefore to the accordion complex~$\AC[\dissection_{\bar Q}]$ and to the slalom complex~$\SC[{\dissection_{\bar Q}}\dual]$.
\item For any pair of dual cellular dissections~$\dissection, \dissection\dual$ of an oriented surface, the non-crossing complex~$\NCC$ is isomorphic to the non-kissing complex~$\NKC[\bar Q_{\dissection, \dissection\dual}]$.
\end{itemize}
\end{theorem}
\begin{proof}
 The first point is a consequence of Proposition \ref{prop:walks=arcs}, Lemma \ref{lem:nonKissing=nonCrossing} and Proposition \ref{prop:accordionsSlaloms}.
 The second point is a consequence of Theorem \ref{thm:bijectionLocallyGentleAndSurfaces} and of the first point.
\end{proof}
